### 2025-03-09 machine-learning.qmd
20250308 - citations

@@

Here is a vignette demonstrating how to impute missing data using `missForest()`: <https://rpubs.com/lmorgan95/MissForest> (archived at: <https://perma.cc/6GB4-2E22>).
Below, we impute the training data (and all data) separately by position.
We then use the imputed training data to make out-of-sample predictions to fill in the missing data for the testing data.
We do not want to impute the training and testing data together so that we can keep them separate for the purposes of cross-validation.
However, we impute all data (training and test data together) for purposes of making out-of-sample predictions from the machine learning models to predict players' performance next season (when actuals are not yet available for evaluating their accuracy).

@@

@@

@@

gp_model_qb <- GPModel(
  group_data = data_train_qb_matrix[,"gsis_id"],
  likelihood = model_likelihood,
  group_rand_coef_data = cbind(
    data_train_qb_matrix[,"ageCentered20"],
    data_train_qb_matrix[,"ageCentered20Quadratic"]),
  ind_effect_group_rand_coef = c(1,1))

gp_data_qb <- gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"])

# Find optimal tuning parameters
opt_params_qb <- gpb.grid.search.tune.parameters(
  param_grid = param_grid_qb,
  params = other_params_qb,
  num_try_random = NULL,
  folds = folds_qb,
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds,
  early_stopping_rounds = 10,
  verbose_eval = 1,
  metric = "mse")

@@

```{r}
gp_model_qb <- GPModel(
  group_data = data_train_qb_matrix[,"gsis_id"],
  likelihood = model_likelihood,
  group_rand_coef_data = cbind(
    data_train_qb_matrix[,"ageCentered20"],
    data_train_qb_matrix[,"ageCentered20Quadratic"]),
  ind_effect_group_rand_coef = c(1,1))

gp_data_qb <- gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"])

@@

```{r}
gp_model_fit_qb <- gpb.train(
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds_qb,
  params = params_qb) # verbose = 0

>>>>

To merge data, we use the `powerjoin` package [@R-powerjoin]:

@@

Here is a vignette demonstrating how to impute missing data using `missForest()`: <https://rpubs.com/lmorgan95/MissForest> (archived at: <https://perma.cc/6GB4-2E22>).
Below, we impute the training data (and all data) separately by position.
We then use the imputed training data to make out-of-sample predictions to fill in the missing data for the testing data.
We do not want to impute the training and testing data together so that we can keep them separate for the purposes of cross-validation.
However, we impute all data (training and test data together) for purposes of making out-of-sample predictions from the machine learning models to predict players' performance next season (when actuals are not yet available for evaluating their accuracy).
To impute data, we use the `missRanger` package [@R-missRanger].

@@

We use the `caret` package [@R-caret].
We use the `parallel` [@R-parallel] and `doParallel` [@R-doParallel] packages for parallel (faster) processing.

@@

To combine tree-boosting with mixed models, we use the `gpboost` package [@gpboost].

@@

gp_model_qb <- gpboost::GPModel(
  group_data = data_train_qb_matrix[,"gsis_id"],
  likelihood = model_likelihood,
  group_rand_coef_data = cbind(
    data_train_qb_matrix[,"ageCentered20"],
    data_train_qb_matrix[,"ageCentered20Quadratic"]),
  ind_effect_group_rand_coef = c(1,1))

gp_data_qb <- gpboost::gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"])

# Find optimal tuning parameters
opt_params_qb <- gpboost::gpb.grid.search.tune.parameters(
  param_grid = param_grid_qb,
  params = other_params_qb,
  num_try_random = NULL,
  folds = folds_qb,
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds,
  early_stopping_rounds = 10,
  verbose_eval = 1,
  metric = "mse")

@@

```{r}
gp_model_qb <- gpboost::GPModel(
  group_data = data_train_qb_matrix[,"gsis_id"],
  likelihood = model_likelihood,
  group_rand_coef_data = cbind(
    data_train_qb_matrix[,"ageCentered20"],
    data_train_qb_matrix[,"ageCentered20Quadratic"]),
  ind_effect_group_rand_coef = c(1,1))

gp_data_qb <- gpboost::gpb.Dataset(
  data = data_train_qb_matrix[,pred_vars_qb],
  categorical_feature = pred_vars_qb_categorical,
  label = data_train_qb_matrix[,"fantasyPoints_lag"])

@@

```{r}
gp_model_fit_qb <- gpboost::gpb.train(
  data = gp_data_qb,
  gp_model = gp_model_qb,
  nrounds = nrounds_qb,
  params = params_qb) # verbose = 0

### 2025-03-09 modern-portfolio-theory.qmd
20250227 - clean up
20250308 - R packages
20250308 - citations

Even so-called experts do not beat the market reliably.
There is little consistency in the performance of mutual fund managers over time.
In the book, "The Drunkard's Walk: How Randomness Rules Our Lives", @Mlodinow2008 reported essentially no correlation between performance of the top mutual funds in a five-year period with their performance over the subsequent five years.
That is, the best funds in a one period were not necessarily the best funds in another period.
This suggests that mutual fund managers differ in great part because of luck or chance rather than reliable skill.
In any given year, some mutual funds will do better than other mutual funds.
But this overperformance in a given year likely reflects more randomness than skill.
That is likely why [a cat beat professional investors in a stock market challenge](http://www.npr.org/blogs/money/2013/01/14/169326326/housecat-beats-investors-in-stock-market-challenge) (archived at <https://perma.cc/R3XU-K6J8>).
That is, "few stock pickers, if any, have the skill needed to beat the market consistently, year after year" [@Kahneman2011, p. 214].
Although our sample size is much smaller with fantasy football projections, there also appears to be little consistency in fantasy football sites' rank in accuracy over time [INSERT], suggesting that the projection sources are not reliably better than each other (or the crowd) over time.

@@

This lesson can also apply to fantasy football.
When assembling a team, you are essentially putting together a portfolio of assets (i.e., team of players).
As with stocks, each player has an expected return (i.e., projection) and a degree of risk.
In fantasy football, a player's risk might be quantified in terms of the [variability](#sec-descriptiveStatisticsSpread) of projected scores for a player across projection sources (e.g., Projection Source A, Source B, Souce C, etc.), or as historical game-to-game [variability](#sec-descriptiveStatisticsSpread).
Variability of projected scores for a player across projection sources could reflect the *uncertainty* of projections for a player.
Variability of historical (actual) fantasy points across games could reflect many factors, including risks due to injuries, situational changes (e.g., being traded to a new team or changes in team composition such as due to the acquisition of new players on the team), game scripts, and the tendency for the player to be "boom-or-bust" (e.g., if they are highly dependent on scoring touchdowns or long receptions for fantasy points).
All things equal, we want to minimize our risk for a given level of expected returns.
That way, we have the best chance of winning any given week.
For the same level of expected returns, higher risk teams might have a few amazing games, but their teams might fall flat in other weeks.
That is, for a given (high) rate of return, [you are best off in the long run (i.e., over the course of a season) with a lower risk team](https://eng.wealthfront.com/2012/01/17/moneyball-using-modern-portfolio-theory-to-win-your-fantasy-sports-league/) compared to a higher risk team (archived at <https://perma.cc/NE35-G6LR>).

@@

However, sometimes having two players on the same team might be beneficial because some positions may be uncorrelated or even negatively correlated, which can also reduce risk.
For instance, the performance of the Tight End and Running Back on the same team tends to be slightly negatively correlated, so it might not be a bad idea to start the Tight End and Running Back from the same team.
For a correlation matrix of all positions on the team, see: <https://assets-global.website-files.com/5f1af76ed86d6771ad48324b/607a4434a565aa7763bd1312_AndyAsh-Sharpstack-RPpaper.pdf> (archived at <https://perma.cc/JQ6G-KSRT>).

@@

@@

@@

<https://eng.wealthfront.com/2012/01/17/moneyball-using-modern-portfolio-theory-to-win-your-fantasy-sports-league/> (archived at <https://perma.cc/JQ6G-KSRT>)

>>>>

Even so-called experts do not beat the market reliably.
There is little consistency in the performance of mutual fund managers over time.
In the book, "The Drunkard's Walk: How Randomness Rules Our Lives", @Mlodinow2008 reported essentially no correlation between performance of the top mutual funds in a five-year period with their performance over the subsequent five years.
That is, the best funds in a one period were not necessarily the best funds in another period.
This suggests that mutual fund managers differ in great part because of luck or chance rather than reliable skill.
In any given year, some mutual funds will do better than other mutual funds.
But this overperformance in a given year likely reflects more randomness than skill.
That is likely why [a cat beat professional investors in a stock market challenge](http://www.npr.org/blogs/money/2013/01/14/169326326/housecat-beats-investors-in-stock-market-challenge) [@Goldstein2013; archived at <https://perma.cc/R3XU-K6J8>].
That is, "few stock pickers, if any, have the skill needed to beat the market consistently, year after year" [@Kahneman2011, p. 214].
Although our sample size is much smaller with fantasy football projections, there also appears to be little consistency in fantasy football sites' rank in accuracy over time [INSERT], suggesting that the projection sources are not reliably better than each other (or the crowd) over time.

@@

This lesson can also apply to fantasy football.
When assembling a team, you are essentially putting together a portfolio of assets (i.e., team of players).
As with stocks, each player has an expected return (i.e., projection) and a degree of risk.
In fantasy football, a player's risk might be quantified in terms of the [variability](#sec-descriptiveStatisticsSpread) of projected scores for a player across projection sources (e.g., Projection Source A, Source B, Souce C, etc.), or as historical game-to-game [variability](#sec-descriptiveStatisticsSpread).
Variability of projected scores for a player across projection sources could reflect the *uncertainty* of projections for a player.
Variability of historical (actual) fantasy points across games could reflect many factors, including risks due to injuries, situational changes (e.g., being traded to a new team or changes in team composition such as due to the acquisition of new players on the team), game scripts, and the tendency for the player to be "boom-or-bust" (e.g., if they are highly dependent on scoring touchdowns or long receptions for fantasy points).
All things equal, we want to minimize our risk for a given level of expected returns.
That way, we have the best chance of winning any given week.
For the same level of expected returns, higher risk teams might have a few amazing games, but their teams might fall flat in other weeks.
That is, for a given (high) rate of return, [you are best off in the long run (i.e., over the course of a season) with a lower risk team](https://eng.wealthfront.com/2012/01/17/moneyball-using-modern-portfolio-theory-to-win-your-fantasy-sports-league) compared to a higher risk team [@Hitchings2012; archived at <https://perma.cc/NE35-G6LR>].

@@

However, sometimes having two players on the same team might be beneficial because some positions may be uncorrelated or even negatively correlated, which can also reduce risk.
For instance, the performance of the Tight End and Running Back on the same team tends to be slightly negatively correlated, so it might not be a bad idea to start the Tight End and Running Back from the same team.
For a correlation matrix of all positions on the team, see: <https://assets-global.website-files.com/5f1af76ed86d6771ad48324b/607a4434a565aa7763bd1312_AndyAsh-Sharpstack-RPpaper.pdf> [@Sherman2021; archived at <https://perma.cc/JQ6G-KSRT>].

@@

We download historical stock prices using the `quantmod` package [@R-quantmod]:

@@

We use the `fPortfolio` package [@R-fPortfolio] to determine the optimal portfolio.

@@

<https://eng.wealthfront.com/2012/01/17/moneyball-using-modern-portfolio-theory-to-win-your-fantasy-sports-league> [@Hitchings2012; archived at <https://perma.cc/JQ6G-KSRT>]

### 2025-03-09 mythbusters.qmd
20250308 - citations

Considerable speculation exists regarding whether players perform better in their last year of their contract (i.e., their "contract year").
Fantasy football talking heads and commentators frequently discuss the benefit of selecting players who are in their contract year, because it supposedly means that player has more motivation to perform well so they get a new contract and get paid more.
To our knowledge, no peer-reviewed studies have examined this question for football players.
One study found that National Basketball Association (NBA) players improved in field goal percentage, points, and player efficiency rating (but not other statistics: rebounds, assists, steals, or blocks) from their pre-contract year to their contract year, and that Major League Baseball (MLB) players improved in runs batted in (RBIs; but not other statistics: batting average, slugging percentage, on base percentage, home runs, fielding percentage) from their pre-contract year to their contract year [@White2014a].
Other casual analyses have been examined contract-year performance of National Football League (NFL) players, including articles in [2012](https://www.4for4.com/2012/preseason/2012-contract-year-players-and-myth-increased-production) (archived [here](https://perma.cc/CT3F-QN5E)) and [2022](https://www.4for4.com/2022/preseason/do-players-perform-better-fantasy-football-contract-year) (archived [here](https://perma.cc/F4F5-7RQZ)).

>>>>

Considerable speculation exists regarding whether players perform better in their last year of their contract (i.e., their "contract year").
Fantasy football talking heads and commentators frequently discuss the benefit of selecting players who are in their contract year, because it supposedly means that player has more motivation to perform well so they get a new contract and get paid more.
To our knowledge, no peer-reviewed studies have examined this question for football players.
One study found that National Basketball Association (NBA) players improved in field goal percentage, points, and player efficiency rating (but not other statistics: rebounds, assists, steals, or blocks) from their pre-contract year to their contract year, and that Major League Baseball (MLB) players improved in runs batted in (RBIs; but not other statistics: batting average, slugging percentage, on base percentage, home runs, fielding percentage) from their pre-contract year to their contract year [@White2014a].
Other casual analyses have been examined contract-year performance of National Football League (NFL) players, including articles in [2012](https://www.4for4.com/2012/preseason/2012-contract-year-players-and-myth-increased-production) [@Bales2012; archived [here](https://perma.cc/CT3F-QN5E)] and [2022](https://www.4for4.com/2022/preseason/do-players-perform-better-fantasy-football-contract-year) [@Niles2022; archived [here](https://perma.cc/F4F5-7RQZ)].

### 2025-03-09 sports-cognitive-psychology.qmd
20250308 - R packages
20250308 - citations

There are a number of [ways in which analytics have changed sports](https://stacker.com/sports/15-ways-analytics-has-changed-sports) (archived at <https://perma.cc/PQ5R-TWFA>).
Here is a summary of some of the key ways that analytics has led to changes.

@@

Although baseball was one of the first major sports to embrace analytics, other sports have been transformed by analytics, as well.
For instance, in basketball, there has been a greater focus on three points and buckets close to the rim (e.g., dunks and layups), with way fewer midrange shots.
Moreover, star players rest more games.
Here is an article on how Shane Battier, who was not the quickest, fastest, or most athletic player, used analytics successfully to guard players who were quicker or more athletic than him: <https://www.nytimes.com/2009/02/15/magazine/15Battier-t.html> (archived at <https://web.archive.org/web/20250219225627/https://www.nytimes.com/2009/02/15/magazine/15Battier-t.html>).

@@

That is, Mike Tomlin, suggested that he does not take into account analytics when making decisions.
Perhaps that is why the Pittsburgh Steelers were voted [one of the least analytically advanced teams](https://www.espn.com/nfl/story/_/id/29939438/2020-nfl-analytics-survey-which-teams-most-least-analytically-inclined) in the NFL in 2020 (archived at <https://perma.cc/R7FA-HGGB>).
Nevertheless, the [Steelers did eventually hire a person focused on analytics](https://www.espn.com/blog/pittsburgh-steelers/post/_/id/14521/why-the-steelers-hired-a-carnegie-mellon-professor-for-advanced-analytics) (archived at <https://perma.cc/W7VE-JZQX>).

A player talent evaluator for the NFL noted that [many people around the league believe that the use of analytics is better suited for baseball than football](https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html) because baseball involves more games, players, and one-on-one matchups (archived at <https://web.archive.org/web/20200803205803/https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html>).
By contrast, player performance in football may be more dependent on teammates and play calls.
The [player talent evaluator noted](https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html), "In football they don't know how to use all the numbers yet...They have the data, they have all these different stats but the people I have talked to aren't completely sure how to use it." (archived at <https://web.archive.org/web/20200803205803/https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html>).
Some dismiss analytics entirely.

@@

For instance, here is a video clip of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops", suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.

![Football Commentator Making Fun of Analytics in Football. From: <https://streamable.com/1hw8>.](images/commentatorOnAnalytics.mp4){width=100%}\

@@

Nevertheless, more and more people around the league are using analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) (archived at <https://perma.cc/7BKP-A4GJ>) and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) (archived at <https://perma.cc/WXE3-53E6>).
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) (archived at <https://perma.cc/49KQ-R785>) and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) (archived at <https://perma.cc/2GRF-8Z5K>).

@@

As depicted in the @fig-goForItPercentageByWinProbChange (which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); archived at <https://perma.cc/S5D8-3NCU>), teams went for it on fourth down nearly twice as often in 2021 compared to 2017, when when their win probability was at least 20% (given the current situation at the start of the given play) and they would increase their win probably by going for it.

@@

Here is an analysis by the New York Times on when to go for it on fourth down: <https://www.nytimes.com/2014/09/05/upshot/4th-down-when-to-go-for-it-and-why.html> (archived at <https://perma.cc/KA9Y-BRUD>).
Here is a fourth down calculator: <https://rbsdm.com/stats/fourth_calculator/>.

@@

After the game, [Feely noted](https://www.nfl.com/news/janikowski-gives-raiders-win-over-jets-in-overtime-09000d5d80bc3910), "I heard the whistle before I started, which is an advantage to the kicker...If you're going to do that, do that before he kicks. I can kick it down the middle, see what the wind does and adjust. It helps the kicker tremendously." (archived at <https://perma.cc/U7SV-UE2E>).

>>>>

There are a number of [ways in which analytics have changed sports](https://stacker.com/sports/15-ways-analytics-has-changed-sports) [@Underwood2019; archived at <https://perma.cc/PQ5R-TWFA>].
Here is a summary of some of the key ways that analytics has led to changes.

@@

Although baseball was one of the first major sports to embrace analytics, other sports have been transformed by analytics, as well.
For instance, in basketball, there has been a greater focus on three points and buckets close to the rim (e.g., dunks and layups), with way fewer midrange shots.
Moreover, star players rest more games.
Here is an article on how Shane Battier, who was not the quickest, fastest, or most athletic player, used analytics successfully to guard players who were quicker or more athletic than him: <https://www.nytimes.com/2009/02/15/magazine/15Battier-t.html> [@Lewis2009b; archived at <https://web.archive.org/web/20250219225627/https://www.nytimes.com/2009/02/15/magazine/15Battier-t.html>].

@@

That is, Mike Tomlin, suggested that he does not take into account analytics when making decisions.
Perhaps that is why the Pittsburgh Steelers were voted [one of the least analytically advanced teams](https://www.espn.com/nfl/story/_/id/29939438/2020-nfl-analytics-survey-which-teams-most-least-analytically-inclined) in the NFL in 2020 [@Walder2020; archived at <https://perma.cc/R7FA-HGGB>].
Nevertheless, the [Steelers did eventually hire a person focused on analytics](https://www.espn.com/blog/pittsburgh-steelers/post/_/id/14521/why-the-steelers-hired-a-carnegie-mellon-professor-for-advanced-analytics) [@Fowler2015; archived at <https://perma.cc/W7VE-JZQX>].

A player talent evaluator for the NFL noted that [many people around the league believe that the use of analytics is better suited for baseball than football](https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html) because baseball involves more games, players, and one-on-one matchups [@Reed2016; archived at <https://web.archive.org/web/20200803205803/https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html>].
By contrast, player performance in football may be more dependent on teammates and play calls.
The [player talent evaluator noted](https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html), "In football they don't know how to use all the numbers yet...They have the data, they have all these different stats but the people I have talked to aren't completely sure how to use it." [@Reed2016; archived at <https://web.archive.org/web/20200803205803/https://www.cleveland.com/browns/2016/01/in_an_nfl_divided_over_analyti.html>].
Some dismiss analytics entirely.

@@

For instance, here is a 2016 video clip of a football commentator, Mike Patrick, making fun of people who compile statistics for informing decision-making in football, calling the people who compile the numbers "guys who wear socks with flip-flops", suggesting that people who compile analytics to make recommendations in football are out of touch with the realities of football and do not have the same on-the-field understanding as the coaches and players.

![Football Commentator Making Fun of Analytics in Football. From: <https://streamable.com/1hw8> (2016).](images/commentatorOnAnalytics.mp4){width=100%}\

@@

Nevertheless, more and more people around the league are using analytics—likely because it works; for examples of articles, see [here](https://www.theringer.com/2018/12/19/nfl/nfl-analytics-revolution) [@Clark2018; archived at <https://perma.cc/7BKP-A4GJ>] and [here](https://www.samford.edu/sports-analytics/fans/2020/The-Future-of-NFL-Data-Analytics) [@Awbrey2020; archived at <https://perma.cc/WXE3-53E6>].
Head Coach Doug Peterson heavily relied on analytics with the Philadelphia Eagles to help them win the 2017 Super Bowl; for more information, see [here](https://www.forbes.com/sites/liamfox/2021/08/12/how-the-nfl-uses-analytics-according-to-the-lead-analyst-of-a-super-bowl-champion/) [@Fox2021; archived at <https://perma.cc/49KQ-R785>] and [here](https://www.nfl.com/news/super-bowl-lii-how-the-2017-philadelphia-eagles-were-built-0ap3000000912753) [@Rosenthal2018; archived at <https://perma.cc/2GRF-8Z5K>].

@@

As depicted in the @fig-goForItPercentageByWinProbChange [which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); @R-nfl4th; archived at <https://perma.cc/S5D8-3NCU>], teams went for it on fourth down nearly twice as often in 2021 compared to 2017, when when their win probability was at least 20% (given the current situation at the start of the given play) and they would increase their win probably by going for it.
We use the `ggtext` package [@R-ggtext] to annotate text:

@@

Here is an analysis by the New York Times on when to go for it on fourth down: <https://www.nytimes.com/2014/09/05/upshot/4th-down-when-to-go-for-it-and-why.html> [@NYT2014; archived at <https://perma.cc/KA9Y-BRUD>].
Here is a fourth down calculator: <https://rbsdm.com/stats/fourth_calculator/>.

@@

After the game, [Feely noted](https://www.nfl.com/news/janikowski-gives-raiders-win-over-jets-in-overtime-09000d5d80bc3910), "I heard the whistle before I started, which is an advantage to the kicker...If you're going to do that, do that before he kicks. I can kick it down the middle, see what the wind does and adjust. It helps the kicker tremendously." [@AP2008; archived at <https://perma.cc/U7SV-UE2E>].
